Realizability-Preserving Two-Moment DG Method for Fermionic Transport \tnoteref{ldrd-support}

### 2018-01-27 Documents/M1/realizableFermionicM1/sections/realizability.tex
Some expressions for moment closures

\subsubsection{Maximum Entropy Closure}
Basic principles
Chernohorsky \& Bludman
Banach \& Larecki

\subsubsection{Kershaw Closure}
Basic principles
Banach \& Larecki

>>>>

Flux factor $h=|\vect{\cH}|/\cJ$
\begin{equation}
  \chi(\cJ,h)=\f{1}{3}+\f{2\,(1-\cJ)\,(1-2\cJ)}{3}\,\Theta\Big(\f{h}{1-\cJ}\Big)
\end{equation}

\subsubsection{Maximum Entropy Closure}
Basic principles
Chernohorsky \& Bludman \cite{cernohorskyBludman_1994}
\begin{equation}
  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny CB}}(x)
  =x^{2}\,\big(\,3-x+3\,x^{2}\,\big)
\end{equation}
Banach \& Larecki
\begin{equation}
  \Theta_{\mbox{\tiny ME}}^{\mbox{\tiny BL}}(x)
  =\f{1}{8}\,\big(\,9\,x^{2}-5+\sqrt{33\,x^{4}-42\,x^{2}+25}\,\big)
\end{equation}

\subsubsection{Kershaw Closure}
Basic principles
Banach \& Larecki \cite{banachLarecki_2017}
\begin{equation}
  \Theta_{\mbox{\tiny K}}^{\mbox{\tiny BL}}(x)=x^{2}
\end{equation}

\subsubsection{Low Occupancy Limit}
